\documentclass{article}
\usepackage{color}
\usepackage[a4paper, margin = 1 in]{geometry}
\usepackage{titling}

\begin{document}

\title{\Huge \textbf{Blake Byer} \vspace{-1.25em}}
\author{}
\date{\today}
\maketitle

\pagenumbering{arabic}
\begin{flushleft}

\section*{Education}

{\large Bachelor of Science in Neuroscience \vspace{0.5em}}\hfill December 2025

\textit{University of Kentucky}

\textit{Minors in Biology, Computer Science, and Mathematics}

\textit{3.95 GPA}

\section*{Experience}

\subsection*{SURE Scholar {\hfill\normalsize\normalfont June 2024 - Present}}
\textit{University of North Carolina at Chapel-Hill \vspace{0.5em}}

SURE Scholar at the University of North Carolina at Chapel-Hill. I am studying rare lysosomal storage diseases
at the intersection of infectious and neurodegenerative diseases.

\subsection*{Research Assistant {\hfill\normalsize\normalfont August 2023 - Present}}
\textit{University of Kentucky \vspace{0.5em}}

Research Assistant at the University of Kentucky College of Medicine. I research polygenic risk scores for 
Alzheimer's disease and statistical fine-mapping for GWAS loci prioritization.

\subsection*{Research Assistant {\hfill\normalsize\normalfont January 2023 - August 2023}}
\textit{University of Kentucky \vspace{0.5em}}

Research Assistant at the Sports Medicine Research Institute at the University of Kentucky College of Health Sciences. 
I contributed to a pilot study that tested wireless motion capture and force-plate insoles for gait retraining in military
personnel. 

\section*{Presentations}
\subsection*{Summer Student Symposium {\hfill\normalsize\normalfont July 2024}}
\textit{University of North Carolina at Chapel-Hill}

Lysosomal storage diseases are not protective against severe COVID-19 infection. Clustering analysis shows the lysosome is implicated in Parkinson's disease.

\subsection*{Great Lakes Bioinformatics Conference {\hfill\normalsize\normalfont May 2024}}
\textit{University of Pittsburgh \vspace{0.5em}}

Averaging polygenic risk scores derived from multiple genome-wide association studies increases predictive accuracy for Alzheimer’s disease.

\section*{Selected Publications}
\begin{enumerate}
\item Averaging polygenic risk scores derived from multiple genome-wide association studies increases predictive accuracy for Alzheimer’s disease. Manuscript in preparation.
\item Clustering analysis shows the lysosome is implicated in Parkinson's disease. Manuscript in preparation.
\end{enumerate}

\end{flushleft}

\end{document}


